ABC - HTW Fits

### 2023-12-01 Model/abc_fit.qmd
larger abc group fits

  # Return results
  list(abc_train_test = abc_train_test, abc_test = abc_test)
}

# Example usage for different models
n_priors=20000
abc_results_varied_exam <- run_abc_fits(avg_dsv, input_layer, output_layer, full_sim_exam, n_prior_samples = n_priors)
abc_results_varied_alt_exam <- run_abc_fits(avg_dsv, input_layer, output_layer, full_sim_alt_exam, n_prior_samples = n_priors)
abc_results_varied_alm <- run_abc_fits(avg_dsv, input_layer, output_layer, full_sim_alm, n_prior_samples = n_priors)

@@

saveRDS(model_cache,here::here(paste0("data/model_cache/abc_group_",format(Sys.time(), "%H_%M_%OS"),".rds")))

>>>>

  # Return results
  tibble::lst(abc_train_test = abc_train_test, abc_test = abc_test, data=data,n_prior_samples,prior_samples,tol, simulation_function, targets=tibble::lst(target_data_train_test, target_data_test))
}

# Example usage for different models
n_priors=200000
abc_results_varied_exam <- run_abc_fits(avg_dsv, input_layer, output_layer, full_sim_exam, n_prior_samples = n_priors)
abc_results_varied_alt_exam <- run_abc_fits(avg_dsv, input_layer, output_layer, full_sim_alt_exam, n_prior_samples = n_priors)
abc_results_varied_alm <- run_abc_fits(avg_dsv, input_layer, output_layer, full_sim_alm, n_prior_samples = n_priors)

@@

saveRDS(model_cache,here::here(paste0("data/model_cache/abc_group_200k_",format(Sys.time(), "%H_%M_%OS"),".rds")))
